Introducing statistics with \\texttt{intRo}

### 2014-12-11 student-paper-competition-2014/paper.Rmd
Blurb about the other software

Upon the release of \texttt{RStudio}'s \texttt{Shiny} [@shiny] it became easy for an R-based analysis to be converted to an interactive web application. This in turn, led to the creation of an introductory statistics application which we call \texttt{intRo}.

\texttt{intRo} offers a number of key advantages over traditional statistics software, which will be discussed at length in this text.

>>>>

Other software has recently been written in an attempt to spur student interest in introductory statistics and R programming. DataCamp's courses are user-friendly ways to learning basic \texttt{R} programming and data analysis techniques. \texttt{Swirl} is a similar interactive tool to make learning \texttt{R} more fun by learning \texttt{R} within \texttt{R} itself. Project MOSAIC has created a suite of tools to simplify the teaching of statistics in the form of an R package. The primary goal of DataCamp and Swirl is to teach \texttt{R} programming, rather than facilitate the learning of introductory statistics. Project MOSAIC's goal is to faciliate this learning, but using the package requires a knowledge of R programming that the introductory student may not have.

Upon the release of \texttt{RStudio}'s \texttt{Shiny} [@shiny] it became easy for an R-based analysis to be converted to an interactive web application. This in turn, led to the creation of an introductory statistics application which we call \texttt{intRo}. \texttt{intRo} offers a number of key advantages over traditional statistics software, which will be discussed at length in this text.
